\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-02-04 tex/paper.tex
Modified introduction

%}}}
\section{Introduction}
Developing larger projects containing static content usually involves using a Content Distribution
Network to be able to scale to a large user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then distributed over the globe when the public requests it. For secret content this can be a
problem and an inconvenience, and that is what this thesis is about. This work examines ways of
enforcing virtual access control on content and groups of content, in the form of containers and
snapshots. A system was developed to make the underlying theory work in practice.

@@

\fix Clarify problem definition and research questions
\newpage
\section{Background}
\subsection{About Uprise}
Uprise is a company based in Uppsala, Sweden. It is an EA studio focussing on creating great gaming
experiences, which means that they are mostly not focussed on the actual gameplay which other EA 
studios like DICE is.

At the moment they are for example very involved with producing the Star Wars Battlefront game by
making menu systems and developing the companion app, Battlefront companion.

@@

@@

All files are also stored directly in MongoDB with the help of GridFS. GridFS chunks the files 
according to the size limit of MongoDB objects, which is currently 4MB. The advantage of this is 
that backups of the Perius state is easily done through a database backup, no separate files 
needs to be backed up. Another advantage that is given by this is that you can retrieve specific 
ranges of a file, although that advantage is not needed in the Perius implementation. The 
disadvantage of using this approach is that when using a non-distributed database it us slower 
to read and write to the database than reading or writing directly to the filesystem. Another 
disadvantage is that to access the files it is needed to go through the database layer in some 
way, instead of accessing the filesystem.

>>>>

%}}}
\section{Introduction}
Developing large projects containing static content usually involves using a Content Distribution
Network to be able to scale to a larger user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then distributed over the globe when the public requests it. For secret content this can be a
problem and an inconvenience, and that is what this thesis is about. This work examines ways of
enforcing virtual access control on content and groups of content, in the form of containers and
snapshots. A system was developed to make the underlying theory work in practice.

@@

\fix Clarify problem definition and research questions
\newpage
\section{Background}
\subsection{About Uprise}
Uprise (formerly known as ESN) is a company based in Uppsala, Sweden. It is an EA studio focussing 
on creating great gaming experiences, which means that they are mostly not focussed on the actual 
gameplay which other EA studios like DICE is. Currently Uprise has a lot of focus on developing 
companion apps and a new form of menu systems.

@@

The copy-on-write system is only used for files as all of the other objects in the system is
basically just meta data and not classed as important, from an data integrity point of view, as the 
actual files themselves.

@@

All files are also stored directly in MongoDB with the help of GridFS. GridFS chunks the files 
according to the size limit of MongoDB objects, which is currently 4MB. The advantage of this is 
that backups of the Perius state is easily done through a database backup, no separate files 
needs to be backed up. Another advantage that is given by this is that you can retrieve specific 
ranges of a file, although that advantage is not needed in the Perius implementation. For
scalability this could be used to retrieve different parts of a file from different servers, 
normal load balancing would probably work better in a system like Perius where no extremely large 
files are expected to be stored.

The disadvantage of using the GridFS approach is that when using a non-distributed database 
it is slower to read and write to the database than reading or writing directly to the filesystem. 
Another disadvantage is that to access the files it is needed to go through the database layer 
in some way, instead of accessing the filesystem.
